### 2018-01-14 latex/MOSIM2018/article.tex
modifications to result tables, added commentary to MOSIM article and changes to heuristic

  In section \ref{sec:soa} we present previous work in this domain. Section \ref{sec:problem} describes with detail the problem, its different elements, conditions and objectives, while the particular dataset used in this study is described in \ref{sec:data}. Section \ref{sec:model} presents a complete MIP formulation to solve the described problem.

  Section \ref{sec:results} shows the results obtained while solving several instances of the problem and finally, section \ref{sec:conclusions} mentions the conclusions obtained from the experimentation and the possible direction of further work in this domain.

@@

  % Here, an alternative model is presented that simplifies the formulation and should permit the inclusion of the rest of constraints without sacrificing optimality.

@@

\section{Datasets}
  \label{sec:data}
  The dataset that was used was provided by the French Airforce and already used by the French Defense Procurement Agency in \cite{Chastellux2017}.
  Based on the information provided, a number of datasets were created with subsets of the main dataset in order to run different tests.

@@

    The main characteristics of the dataset are the following. 11 tasks, 127 resources.
    Most tasks demand between 1 and 8 resources per month. The biggest and second biggest tasks demand 50 and 20 resources respectively each month.
    More details in table \ref{tab:tasks}.
    Candidates are calculated based on each task's requirements matching the candidate's capabilities.

@@

    All maintenances take 6 months (periods). Each maintenance provides with 1000 hours of usage time to the resource and a resource can be without maintenance for a maximum of 60 periods. The nominative capacity for maintenance is 18 resources at any given time.

@@

      The distribution of initial usage times is shown in the figure \ref{fig:histogramUsage}. It can be seen that the aircraft do not necessarily follow an horizontal line.

@@

  All tests were run on a 64 bit Ubuntu 16.04 workstation with 16GB of RAM and Intel i7-6700HQ CPU \@ 2.60GHz x 8 processor.
  Several experiments were done with the MIP formulation. Table \ref{tab:instance} shows the characteristics of each instance. 
  Most of the columns describe the size of the instance: number of periods, number of tasks and number of assignments.
  The assign column indicates the number of assignments that are needed to be done to all the task-periods.

  Table \ref{tab:summary} gives an overview on the results obtained for each of the executed instances.

@@

  \caption{Solution details on the progress of the lower bound. "id" shows the name of the instance; "root" the relaxation before cuts; "b. cuts" the relaxation after the cuts; "bound" the relaxation at the time limit; "cuts (\#)" the number of cuts; and "cuts (s)" the time the cuts took in seconds}
  \vspace{-0.5cm}
  \label{tab:results}
  \end{center}
  \end{table}

@@

  \caption{Solution details on the progress of the integer solution. "id" shows the name of the instance; "first" is the first solution integer found; "sol. cuts" the solution after the cuts; "last" is the last solution found at the time limit; "cuts (\#)" the number of cuts; and "cuts (s)" the time the cuts took in seconds}
  \vspace{-0.5cm}
  \label{tab:results2}
  \end{center}
  \end{table}

  Figure \ref{fig:progress} shows an example of progress for instance with id=1817.

@@

@@

  \caption{Comparison of instances where variations on the weight of its two objectives has been done. Instance id=1331.}
  \vspace{-0.5cm}
  \label{tab:multiobj}
  \end{center}
  \end{table}

@@

  The results show that a direct exact method to solve the whole dataset may not be ideal. Although medium size instances have been solved, the complete dataset is not solved in a reasonable time for more horizons bigger than 10 periods. Still, the analysis on the progress of the lower bound shows that further work can be done to improve the model in order for it to have a better relaxation. One possibility is replacing the constraints that count the remaining usage time and elapsed time for more tighter constraints. Another possibility is slightly changing the objective function so it can measure more gradually the smoothness of the objective and help get better lower bounds.

  Regarding the multi-objective nature of the problem, the bi-objective analysis appears to indicate the existence of a small number of solutions that are Pareto optimal. If this is the case, an iterative approach that explores these solutions could be done. To confirm the true number of solutions, an analysis using epsilon constrains should follow. Further tests with different, bigger, instances could also reveal more information regarding the relation between the two objectives. Improvement in the mono-objective modeling could also lead to producing non-dominated solutions. In addition to this, new objectives could be included into the analysis, such as smoothing the remaining usage time among periods instead of doing it only in the last period.

  Another possible reason for the difficult in solving big instances could be the quantity of symmetries among candidates for each task: there exist a very big number of possible candidates to be potentially assigned for each task with respect with the actual needed resources of the task. This could be handled by assigning priorities to some combinations of resource-task or by limiting the number of candidates that can be assigned to each task by some heuristic that clusters resources with tasks.

  As new constraints are added, such as minimum durations for assignments and the possibility to "store" resources for a predefined time, the present instances will grow bigger still. This, of course, will require new better techniques to decompose the problem into smaller problems using heuristics or take a decomposition approach such as Column Generation.

>>>>

  This paper presents a specific version of the Flight and Maintenance Problem, which we call Military Flight and Maintenance Problem. We provide a description of the problem, a mathematical formulation to obtain quality solutions for a bi-objective optimization function and experimental results to show both the quality of the solutions and the limitations of the technique.

  The article is structured as follows:

  Section \ref{sec:problem} describes with detail the problem, its different elements, conditions and objectives. We also make a review of previous work done in the subject in section \ref{sec:soa} where we compare the addressed problems with our own and explain the differences.

  Later, in section \ref{sec:data}, the specific dataset at hand is described. Section \ref{sec:model} presents a complete MIP formulation to solve the described problem and section \ref{sec:results} shows the commented results obtained while solving several instances of the problem based on the provided dataset.

  Finally, section \ref{sec:conclusions} mentions the conclusions obtained from the experimentation and the possible direction of further work.

@@

  Here, an alternative model is presented that simplifies the formulation and should permit the inclusion of the rest of constraints without sacrificing optimality.

@@

\section{Datasets}
  \label{sec:data}
  The dataset being used was provided by the French Airforce and already used by the French Defense Procurement Agency in \cite{Chastellux2017}.
  Based on the information provided, a number of instances were created as subsets of the main dataset in order to run different experiments.

@@

    There are a total of 12 tasks.
    Most tasks demand between 1 and 8 resources per month. The biggest and second biggest tasks demand 50 and 20 resources respectively each month.
    More details of task differences are found in table \ref{tab:tasks}.
    Candidates are calculated based on each task's requirements matching the candidate's capabilities.

@@

    All maintenances take 6 months (periods). Each maintenance provides with 1000 hours of usage time to the resource and a resource can be without maintenance for a maximum of 60 consecutive periods. The nominative capacity for maintenance is 18 resources at any given time.

@@

    There are 127 resources in total. Each one with its functionalities and past assignments.
    The distribution of initial usage times is shown in the figure \ref{fig:histogramUsage}. It can be seen that the aircraft do not necessarily follow an horizontal line.

@@

  All tests were run on a 64 bit Ubuntu 16.04 workstation with 16GB of RAM and Intel i7-6700HQ CPU \@ 2.60GHz x 8 processor.
  Several experiments were done with the MIP formulation. Table \ref{tab:instance} shows the characteristics of each experiment. The main differences between instances is the number of tasks and the number of periods.

  Table \ref{tab:summary} gives an overview on the results obtained for each of the executed instances. As can be seen, smaller instances are solved up to optimality while medium size ones are stopped after one hour.

@@

  \caption{Solution details on the progress of the lower bound. "id" shows the name of the instance; "root" the relaxation before cuts; "b. cuts" the relaxation after the cuts; "bound" the relaxation at the time limit; "cuts (\#)" the number of cuts; and "cuts (s)" the time the cuts took in seconds.}
  \vspace{-0.5cm}
  \label{tab:results}
  \end{center}
  \end{table}

  The table \ref{tab:results2} show the progress of the integer solution for each instance. For more detail of this progress, figure \ref{fig:progress} shows an example of progress for instance with id=1817. It can be seen that initial solutions are quite big in comparison with the optimal.

  For two, rather small, instances the solver was able to find an optimal solution before starting to branch. In these two instances, the missing values have been replaced by "-1".

  These results show how the branching is not providing with much improvement in increasing the lower bound or finding better integer solutions. This hints into a possible reason for the difficult in solving big instances: the quantity of symmetries in the model, represented as candidates for each task: there exist a very big number of possible candidates to be potentially assigned for each task with respect with the actual needed resources for the task. This reduces the capacity of the branching the solver does by making it explore many nodes that are really almost equivalent.

@@

  \caption{Solution details on the progress of the integer solution. "id" shows the name of the instance; "first" is the first solution integer found; "sol. cuts" the solution after the cuts; "last" is the last solution found at the time limit.}
  \vspace{-0.5cm}
  \label{tab:results2}
  \end{center}
  \end{table}

@@

    The bi-objective analysis appears to indicate the existence of a small number of solutions that are Pareto optimal. If this is the case, an iterative approach that explores these solutions could be done. Improvement in the mono-objective modeling could also lead to producing non-dominated solutions.

@@

  \caption{Comparison of instances where variations on the weight of its two objectives has been done. Instance id=1331. All experiments were solved to optimality.}
  \vspace{-0.5cm}
  \label{tab:multiobj}
  \end{center}
  \end{table}

@@

  The results show that a direct exact method to solve the whole dataset may not be ideal. Although medium size instances have been solved, the complete dataset is not solved in a reasonable time for more horizons bigger than 10 periods. Still, the analysis on the progress of the lower bound shows that further work can be done to improve the model in order for it to have a tighter, better relaxation. One possibility is to replace the constraints that count the remaining usage time and elapsed time for tighter constraints. Another possibility is slightly changing the objective function so it can measure more gradually the smoothness of the objective and help get better bounds.

  Regarding the multi-objective nature of the problem, to confirm the true number of solutions, an analysis using epsilon constrains should follow. Further tests with different, bigger, instances could also reveal more information regarding the relation between the two objectives. In addition to this, new objectives could be included into the analysis, such as smoothing the remaining usage time among periods instead of doing it only in the last period.

  Regarding the branching and symmetries: this could be handled by assigning priorities to some combinations of resource-task or by limiting the number of candidates that can be assigned to each task by some heuristic that clusters resources with tasks. Finally, arbitrarily preassigning (fixing) the final state (in terms of remaining usage time) to each resource could also help break those symmetries.

  As new constraints are added, such as minimum durations for assignments and the possibility to "store" resources for a predefined time, it is predicted that the present instances will grow bigger. This, of course, will require new and better techniques to decompose the problem into smaller problems using heuristics or to take a decomposition approach such as Column Generation.

  Finally, this work presents a first step useful into the solving of the Military Flight and Maintenance Planning. The model presented provides already good initial solutions and also the potential of solving even bigger, more complex problems.
